### 2013-01-08 edupar-13/410.tex
Move outcomes to after landslide
write about grading

@@

%=== Outcomes ===%
\subsection{Outcomes}

\framebox{Some text should go here!}

>>>>

%=== Grading ===%
\subsection{Grading}

Pebbles kernels are graded in three ways: passing the ``hurdle'', running an automated test suite, and undergoing manual inspection by course staff.

\subsubsection{Hurdle}
%% TODO: Dave, write about the criteria (and what it means, i.e., "getting a shell up and running, getting processes to exit")
The hurdle is a set of criteria that Pebbles implementations must meet to be considered sastisfactory
(TODO: what are they?).
Towards the end of the kernel project, students fill out the ``hurdle form'', a checklist of these criteria.
Students who pass the hurdle are permitted to turn in their kernels and move on to the final, shorter, project; otherwise, they must spend the remaining two weeks continuing to work towards the hurdle.
The hurdle criteria constitute 50\% of the kernel project's grade.

\subsubsection{Automated tests}
We run submitted kernels in an automated testing harness, called ``Fritz''.
On each kernel, Fritz runs a number of userspace programs which test functionality ranging from the basic process lifecycle, to robustness against corner-case security vulnerabilities, to long-term stability under large stress tests.
Passing Fritz's tests constitutes 30\% of the kernel project's grade.

Unfortunately, due to the nondeterministic nature of many common bugs in student code, Fritz is unable to verify any submission's correctness with complete certainty.
(The hit-or-miss nature of Fritz's bugfinding motivated our work on Landslide.)

\subsubsection{Manual inspection}
Finally, both to make up for Fritz's incompleteness and to provide personalized human feedback, each student kernel is manually graded by a member of course staff.
The instructors and teaching assistants print out each group's submitted kernel and mark it with red ink, auditing the code for code style, architectural issues, race conditions, and preemptibility.
After the inking process, each group meets with the staff member who graded them for an hour-long ``kernel interview'', essentially a debriefing in which any final misconceptions the students might have can be rectified.
Staff discretionary points constitute 20\% of the kernel project's grade.

@@
